\LaTeXe\ guide for the Journal of Functional Programming

### 2019-11-01 papers/jfp/8-engineering.tex
Add a paragraph on concurrent output modification

>>>>

Build systems that run continuously are also more likely to encounter errors
caused by concurrent modification of \emph{build outputs}. For example, if an
output file is checked into the source repository then downloading a new
version of the file can interfere with the build task producing it, resulting
in a corrupted output that the build system will be unable to detect. This
problem can be solved by ensuring that tasks have an \emph{exclusive access}
to their outputs, e.g. by sandboxing the tasks whose outputs can be modified
externally.
